### 2019-07-22 draft_charts.Rmd
Drop about from title 1 and the note in chart 8.

# create the output plot
plotr(titler("A typical Xennial retiree will receive about 24 percent more net income than a typical retiree born 40 years earlier", width = 60),
      subtitler("Median annual per capita after-tax family income at age 70 (constant 2018 dollars)"),
      chart2,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("This income measure includes Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, interest, dividends, capital gains, and retirement account withdrawals, minus payroll taxes, federal and state income taxes, and Medicare surtaxes. The analysis computes a per capita measure by dividing total family income by two for married people and assumes that scheduled Social Security benefits are paid."),
      heights = c(3.2, 1.5, 30, 1, 1, 4))
```

@@

# create the output plot
plotr(titler("For Xennials, women’s median Social Security benefits at\nage 70 will rise to 85 percent of the median for men", width = FALSE),
      subtitler("Median annual Social Security income at age 70 (constant 2018 dollars)"),
      chart3b,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("Analysis assumes that promised Social Security benefit payments will continue."), 
      heights = c(3.5, 1.5, 30, 1, 1, 1))
```

>>>>

# create the output plot
plotr(titler("A typical Xennial retiree will receiv 24 percent more net income\nthan a typical retiree born 40 years earlier", width = FALSE),
      subtitler("Median annual per capita after-tax family income at age 70 (constant 2018 dollars)"),
      chart2,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("This income measure includes Social Security, earnings, defined-benefit pensions, Supplemental Security Income, other government benefits, interest, dividends, capital gains, and retirement account withdrawals, minus payroll taxes, federal and state income taxes, and Medicare surtaxes. The analysis computes a per capita measure by dividing total family income by two for married people and assumes that scheduled Social Security benefits are paid."),
      heights = c(3.2, 1.5, 30, 1, 1, 4))
```

@@

# create the output plot
plotr(titler("For Xennials, women’s median Social Security benefits at\nage 70 will rise to 85 percent of the median for men", width = FALSE),
      subtitler("Median annual Social Security income at age 70 (constant 2018 dollars)"),
      chart3b,
      caption,
      sourcer("DYNASIM4, ID963."),
      noter("The analysis assumes that promised Social Security benefit payments will continue."), 
      heights = c(3.5, 1.5, 30, 1, 1, 1))
```
